Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-19 03_Preliminary_analysis.Rmd
conflicting labels

```{r Fungicide_x_nSprays_tble, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

```{r Fungicide_x_nSprays_tble, message=FALSE}

>>>>

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

```{r Fungicide_x_nSprays_tble1, message=FALSE}
